Twisted 11-dimensional supergravity, I

### 2021-09-15 draft.tex
suco

\input{symmetry}

%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.

\section{Twisted supergavity on AdS space}

\subsection{Superconformal algebras}

\begin{prop}
The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
\end{prop}

\subsection{The ${\rm AdS}_7 \times S^4$ background}

Choose a splitting 
\[
\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
\]
and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.

The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
\[
\lie{sl}(4) \oplus \lie{sl}(2) .
\]
which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.

The embedding of the bosonic piece can roughly be described as follows. 
The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.

\begin{itemize}

\item
The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
\[
\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
\]

\item
The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
rotations
\[
A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
\]

\item
The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
\[
\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
\] 
Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
\item 
The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
\[
z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\] 
Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
\item 
The bosonic summand $\lie{sl}(2)$ is mapped to the triple
\[
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\]
\end{itemize}

The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
Then the odd part decomposes as
\[
L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
\]

\begin{itemize} 
\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
It is mapped to the fields 
\[
z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
\] 
\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
It is mapped to the fields
\[
\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
\]
\end{itemize}

\subsection{The ${\rm AdS}_4 \times S^7$ background}

\parsec[]
\brian{discuss coupling}

We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
\[
\CC_z \times \CC^4_w \times \RR .
\]
Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.

The differential form which sources the brane is an element
\[
\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
\]
Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
\[
\dbar \til{F} = N \delta_{w=0} 
\]
where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.

Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
\[
F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
\]
For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.

\begin{lem}
The field 
\[
F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
\]
satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
\[
\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
\]
where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
\end{lem}

\begin{proof}
The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
\end{proof}

Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.

\begin{itemize}
\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
\[
\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\]
Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
\[
\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
\]
\end{itemize}

The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
\[
(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
\]

\begin{itemize}
\item 
The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
It is mapped to the fields: 
\[
\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
\] 
\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
It is mapped to the fields: 
\[
\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
\] 
\end{itemize}

\subsection{Supersymmetric indices}

\brian{SU(5) and SU(2) character calculations}

\section{Dimensional reduction and compactifications} 
\include{dimred}

\subsection{The theory on a three-fold}

>>>>

\input{matrix}

\input{susy}

%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists. 
\input{suco}
